 \documentclass[DIN, pagenumber=false, parskip=half,fromalign=right, fromphone=false,fromemail=false, fromurl=false,fromlogo=false, fromrule=false]{scrlttr2}
\usepackage[mac]{inputenc}
\usepackage[ngerman]{babel}
\RequirePackage{graphicx}
\setkomafont{footnote}{\normalcolor \sfseries} 
 \setkomavar{date}{\sffamily \today}
\setkomavar{fromname}{  \sffamily Dr.\ Chaitanya S. Gokhale}
\setkomavar{fromaddress}{ \sffamily  Max-Planck Institute for Evolutionary Biology \\ August-Thienemann-Str. 2, 24306 Plön, Germany}
\setkomavar{backaddress}{\sffamily Dr.\ Arne Traulsen, August-Thienemann-Str. 2, 24306 Plön} 
\setkomavar{fromemail}{\sffamily gokhale@evolbio.mpg.de}

\setkomavar{subject}{Submission to Evolution}
 

\begin{document}
\sffamily



\begin{letter}{
\sffamily
Prof.\ Dr.\  Daphne J. Fairbairn\\
Editor-in-Chief\\
Evolution\\
Wiley-Blackwell, John Wiley and Sons, Inc.\\
350 Main Street, Commerce Place \\
Malden MA, 02148\\
USA
}              
\opening{\sffamily \vspace{-0.5cm} Dear Prof. Fairbairn,}
\vspace{-0.3cm}
Please find enclosed our manuscript titled “Mutualism and evolutionary multiplayer games: Revisiting the Red King”.

Evolutionary game theory has become is one of the most successful modeling approaches in biology. 
Our manuscript applies the recent theoretical developments in multiplayer evolutionary game theory to the idea of mutualistic interactions. 
Almost a decade ago Bergstrom and Lachmann proposed a radical concept called “Red King effect” based on two player interactions, where the slowest runner runner can win the evolutionary race. 
Our manuscripts builds on that research but uses multiplayer games. 
We show that the Red King effect can become weaker or stronger in a multiplayer setting.
Moreover, we depict how such nonlinear properties of mutualistic relationships can be explored and how they can
shape the evolutionary outcome.

As a handling editor, we would like to propose Reinhard Bürger.
%He has coauthored seminal papers on ecosystem dynamics and stability and 
We are convinced that the subject of the manuscript fits his domain of interest. %Therefore, he would be the perfect editor to handle a manuscript on this subject. 
An excellent alternative would be Aneil Agrawal.

We hope that you are able to consider our manuscript for publication as we are confident that it matches the interests of the readership of Evolution.

With kind regards,\\
Chaitanya S. Gokhale and Arne Traulsen
\end{letter}

\end{document}